---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BAQM

<!-- badges: start -->
[![R-CMD-check](https://github.com/CPA-wrk/BAQM/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/CPA-wrk/BAQM/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

<!-- R_LIBS_USER='/Users/peter/Library/Caches/org.R-project.R/R/renv/library/BAQM-8c6b0fb8/macos/R-4.5/aarch64-apple-darwin20' -->
  
BAQM supplies functions developed by Babson College instructors
for AQM 1000 and AQM 2000 courses using R in the curriculum.
The primary functions provide:

* `stat_desc()` - summary descriptive statistics for data frames, allowing both numeric and factor variables, in both wide and long formats.
* `summary.lm()` - expanded statistics and enhanced formatting to summarize linear model results.
* `lm_plot.4way()` - multiple diagnostic plots for linear models using ggplot, including a 4-in-1 summary graphic.
* `print.summary.regsubsets()` - compact "best subsets" linear model reports for analytics from the `regsubsets` function of the leaps package. Note that this BAQM package must
be loaded (using `library(BAQM)`) **after** the leaps package is loaded.

## Installation

You can install the development version of BAQM
from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
# pak::pak("CPA-wrk/BAQM")
```

## Example

These examples use the built-in R data sets `iris`, `swiss`, and `mtcars`, and
show:

* brief statistical summaries of data sets `iris` and `swiss`,
* a concise best-subsets report for regression modeling of Fertility in
  `swiss`,
* expanded statistical summaries for linear models of Sepal Length in
  `iris` and miles per gallon in `mtcars`, and
* a 4-way diagnostic plot for the `mtcars` model.

(Variable names are truncated in `swiss` to narrow the output.)

```{r example}
library(leaps)
library(BAQM)
#
stat_desc(iris) # Includes non-numeric variable
#
names(swiss) # Show original variable names
names(swiss) <- substr(names(swiss), 1, 4) # Narrows output
stat_desc(swiss)
regs <- regsubsets(Fert ~ ., data = swiss, nbest = 3)
summary(regs)
#
mdl <- lm(Sepal.Length ~ ., data = iris)
summary(mdl)
#
mdl <- lm(mpg ~ hp + qsec, data = mtcars)
summary(mdl)
lm_plot.lst <- lm_plot.4way(mdl)
lm_plot.lst$p_4way
```
