---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BAQM

  <!-- badges: start -->
  [![R-CMD-check](https://github.com/CPA-wrk/BAQM/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/CPA-wrk/BAQM/actions/workflows/R-CMD-check.yaml)
  <!-- badges: end -->

<!-- R_LIBS_USER='/Users/peter/Library/Caches/org.R-project.R/R/renv/library/BAQM-8c6b0fb8/macos/R-4.5/aarch64-apple-darwin20' -->
  
BAQM supplies functions developed by Babson College instructors
for AQM 1000 and AQM 2000 courses using R in the curriculum.
The primary functions include:

* `stat_desc()` - a function to produce descriptive statistics for data frames
* `summary.lm()` - a function to summarize linear model results
* `lm_plot.4way()` - a function to produce diagnostic plots for linear models
* `print.summary.regsubsets()` - a function to format a "best subsets" report created by the `regsubsets` function from the leaps package

## Installation

You can install the development version of BAQM
from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
# pak::pak("CPA-wrk/BAQM")
```

## Example

Here are summaries of built-in R data sets `swiss` and `iris`, with 

* a best-subsets analysis of modeling Fertility in `swiss` and
* a linear model with analytics of Sepal Length in `iris`.

(Variable names are truncated in `swiss` to narrow the output.)

```{r example}
# library(BAQM)
names(swiss) # Show original variable names
names(swiss) <- substr(names(swiss), 1, 4) # Narrows output
stat_desc(swiss)
#
regs <- leaps::regsubsets(Fert ~ ., data = swiss, nbest = 3)
print.summary.regsubsets(regs)
#
stat_desc(iris) # Includes non-numeric variable
#
mdl <- lm(Sepal.Length ~ ., data = iris)
print.summary.lm(summary.lm(mdl))
lm_plot.4way(mdl)
```
